HyperLogLog: Exponentially Bad in Adversarial Settings

### 2020-04-27 docs/HLL_exp_bad/main.tex
work on adv setting

\section{Introduction}
Naive approaches to computing the cardinality of a big data set, such as sorting the elements or simply maintaining the set of unique elements seen, are impractical at scale. The HyperLogLog algorithm (HLL henceforth)~\cite{loglog,hll2} is today the most widely used cardinality estimator. It is increasingly used in settings where adversaries may have  incentives to manipulate the estimate made by the algorithm. For example,~\cite{portscanhll} proposes its use for detecting network scanning attacks, while Facebook engineers have reported~\cite{fbhll} that they use HLL for estimating the number of active users. These applications demand a careful evaluation of the performance of HLL under adversarial input.

@@

\section{Overview of HLL}\label{sec:overview}
\subsection{The Algorithm}
HLL~\cite{loglog,hll2} is a streaming algorithm based on the key observation that, for a stream of randomly distributed values represented as bit-strings of some fixed length, if we observe a value with the maximum of $k$ leading zero-bits, then the cardinality of the stream (i.e.\ the number of distinct values it contains) is likely to be on the order of $2^{k+1}$. In practice, to ensure a uniform distribution, the stream values are first processed by a hash function $h$ before the leading bits are inspected. So to estimate the cardinality of a stream, we need only store a representation of $k$, the length of the largest observed string of leading zero-bits for numbers in the stream. This provides a very compact mechanism for estimating the stream cardinality -- if the true cardinality is $N$, then just $\log\log(N)$ bits are needed to store the estimate.

This simple approach suffers from large variance in the estimation. In order to improve the estimate, we can use many estimators in parallel instead of one, and average the results. Each estimate is stored in its own bucket. The collection of buckets is referred to as the HLL \emph{sketch}. To map a value $x$ to one of $2^n$ buckets, \cite{loglog} suggests using the first $n$ bits of $h(x)$ as a bucket index, and then computing the longest sequence of leading zero bits on the remaining $\ell$ bits of $h(x)$ (so that the output length of $h(\cdot)$ is $n+\ell$). Estimators from all buckets are averaged using the harmonic mean and scaled by a constant $\alpha$, where $\alpha$ empirically computed to correct a systematic multiplicative bias. As result, HLL is able to estimate cardinalities greater than $10^9$ with a typical standard error of 2\%, using only 1.5 kB of memory~\cite{add-ref-for-this-claim}.

@@

\subsection{Applications}
For completeness and motivation, we provide examples of concrete uses of HLL:
\begin{itemize}
    \item Cardinality estimation provides a significantly faster way for Facebook to compute statistics on their users. They use HLL to find out how many distinct people visited their website in the past week~\cite{fbhll}.
    \item HLL has been proposed as a solution to detecting Denial-of-Service attacks~\cite{portscanhll} (this paper actually uses a variation on HLL called \emph{sliding HLL}~\cite{slidinghll} which estimates the cardinality over a moving time window). Specifically, HLL is used to count how many different ports are used as destination port over all packets received, as an attempt to identify when a port scan attack is underway.
        \item HLL has been implemented in network switches to approximate the number of distinct packets in traffic flows and overcome the switch resource limits~\cite{flexswitch}. The number of unique flows traversing a switch can then be used to provide a better congestion control protocol.
        \end{itemize}

@@

\subsection{Adversarial Setting}
We model three distinct adversarial scenarios based on the adversary's knowledge and capabilities. For all of them, we assume that the sketch already contains some existing data from honest users to simulate a real-life setting. Among the scenarios, S4 makes the strongest assumptions about the adversarial capabilities, since it combines the knowledge of adversaries from S1 and S2. \kenny{Not really! Because S1 is actually quite unrealistic, as we will argue below.}

\begin{itemize}
\item[S1:] The adversary has black-box access to the HLL in use -- that is, the adversary can ask for the HLL's cardinality estimate at any point in time, and so is able to check the effect on the cardinality estimate when inserting an item. \kenny{TODO: clarify more what this is terms of a ''test oracle''; its stronger than described because the adverary can test the effect of an insertion without making the insertion!s}
\item[S2:] The adversary has access to the details of the HLL implementation, i.e., the adversary knows the number of buckets $2^n$ and the hash function $h$ in use, but is otherwise ``blind''. In particular, an S2 adversary does not have access to the values of the HLL cardinality estimate at any point in its attack.
\item[S3:] \kenny{TODO: The external attacker from~\cite{cardestprivacy}  described in terms of oracles.}
\item[S4:] the adversary has direct access to the HLL in use and all its internals, i.e., the number of buckets, the hash function $h$, and also the contents of each bucket in the HLL sketch. Recall that these buckets hold the intermediate estimators that are averaged in a later step to compute the final cardinality estimate. Again, an S4 adversary does not have access to the values of the HLL cardinality estimate at any point in its attack, but it can compute these values for itself (assuming its attack proceeds without input from other users being added to the HLL sketch in parallel with the attack).
\end{itemize}

Scenarios S1 and S2 are presented as M2 and M1, respectively, in~\cite{hllvuln}. We do not put our focus on S1 as this previous work in~\cite{hllvuln} fully exploits this scenario. Their attack works as follows: ``after each insertion the cardinality is checked and the items which do not increment the HLL estimate are retained''. It is unclear what this means in practice, since after insertion into the HLL, an item cannot usually be removed by the adversary. \kenny{Mathilde: can you think about this sentence that I added? Do we need to rewrite S1? The scenario does not really make sense at all in practice. I think we might use this to beat up the other paper a bit more.}

@@

We start by presenting our attack in scenario S2, providing much stronger results than the corresponding attack of \cite{hllvuln}, and then use the additional information the adversary has access to in scenario S4 to make the attack even more powerful.

@@

\noindent\paragraph{Scenario S2:} The adversary knows $h$ so it can adjust fields in the item $x$ it is trying to insert and keep only those for which the $\ell$ rightmost bits of $h(x)$ start with a one bit. In this case, the number of leading zero bits computed by the estimator of the destination bucket is always zero, so the estimator of this bucket is unlikely to be updated and the averaged approximate cardinality is likely to be left unchanged. For example, in the scenario of \cite{portscanhll}, the adversary could change the source port of his IP packet until it is satisfied with its hash value. Given sufficient flexibility in the input $x$, the adversary can insert many items into the HLL without increasing the cardinality markedly, by repeatedly sampling from the input domain.

\noindent\paragraph{Scenario S4:} The adversary can adopt the same strategy as for S2, but make the attack more efficient and reduce the sampling requirements with the additional information available in this scenario (namely, the count values per bucket in the HLL sketch). So, it can allow some leading zero bits in the $\ell$ rightmost bits of $h(x)$ so long as this does not increase the current bucket estimate. In other words, if $h(x)$ is mapped to the $i$-th bucket with estimated cardinality $2^{c_i + 1}$ (because a value with $c_i$ leading zeroes was previously observed for this bucket), then, instead of the strict restriction of having a one bit in the first position in the $\ell$ rightmost bits of $h(x)$, the adversary is satisfied when there is a one bit in any of the first $c_i+1$ positions in this substring. In case the adversary hits an empty bucket (for which the estimator is 0), it must skip that bucket completely. Under these conditions, the estimators in the buckets are never updated, and there is no effect on the cardinality estimate made by HLL.  A special case arises when the HLL is completely empty at the beginning of the attack; here the adversary is forced to increase the estimate in at least one bucket, but with sampling this can obviously be done in such a way as to increase the HLL estimate to $2$ in a single bucket, leaving all the other buckets untouched.

@@

We assumed so far that there are already values coming from other honest users' data in the HLL. We now remove this assumption. The blind adversary in scenario S2 has no way to detect that he is attacking an empty HLL and cannot adapt his strategy, so all buckets that are hit will update their estimator once to $2^{0+1}=2$ items, leading to a final cardinality approximation of $\alpha2^{n+1}$ regardless of the number of items the adversary inserts. However, the adversary in S4 is able to detect that all buckets are empty and adapt his attack accordingly. The adversary can now target and fill one bucket only. This requires fixing $n+1$ bits of $h(x)$ for each input $x$, allowing the adversary to ``hide'' $2^{t-n-1}$ elements while keeping the HLL cardinality estimate to 1. Other work/cardinality-estimate trade-offs are of course possible.

@@

As a proof-of-concept, we implemented our attacks against the HLL implementation from \cite{clahll}. The attack code is available at \href{https://github.com/PizzaWhisperer/HLLVuln}{\textit{\url{https://github.com/PizzaWhisperer/HLLVuln}}}. For simplicity, our items are 4-character long ASCII strings, giving us up to 7,311,616 distinct items that can be inserted. We choose $h$ to be the 32-bit Murmur3 hash function from \cite{murmur3code}. \kenny{Why do we get to choose $h$? Isn't it fixed by the specific implementation we are attacking?} We create an HLL sketch using $2^n = 256$ buckets and initialize it with 1,000 random items representing honest users' data.

@@

Those empirical results confirm our impact analysis on several points. First, when attacking a sketch already containing some items, we can see that the adversary is able to hide approximately half of the items' set under S2, and around 83\%%( $205$'$000 \approx 250'000 \times 0.82 \approx 250$'$000\times(1-\frac{1}{2\times H_c})$, with $H_c\approx\frac{1'000}{256}=3.9$).
$\approx (1-\frac{1}{2\times H_c})$ with $H_c\approx\frac{1'000}{256}=3.9$, under S4.
Secondly, when attacking an empty sketch, the final cardinality estimate is always exactly 367 $=\alpha2^{n+1}$ with $\alpha = 0.72$ as specified by the Eq. (29) of \cite{hll2} or 1 in respectively S2 and S4.

To assess the efficiency of our attacks, we can confront our results from Tab. \ref{table:tab2} with the attack presented in the Section 5.1 of \cite{hllvuln}, where they target the Redis \cite{redishll} open-source implementation of HLL and perform the attack against an empty sketch. Given a set of 250'000 items, the adversary could choose ``74'390 distinct items and obtain an HLL estimate of only 15'780`` achieving a five-fold reduction from the true cardinality. In comparison, the adversary following our strategy is able to add 125'000 distinct items while keeping the estimate at 367, demonstrating a reduction by a factor of 340.

\begin{table}[h]
\caption{Result of the attacks over 30 iterations}
\begin{tabular}{| m{8.5em} | m{4em} | m{4em} | m{4em} | m{4em} |}
    \hline
    \textbf{Scenario} & \multicolumn{2}{c|}{S2} & \multicolumn{2}{c|}{S4} \\ \hline
    \textbf{Initial data?} & yes & no & yes & no \\ \hline
    \textbf{Original Est. Card.} & 1'000 & 0 & 1'005 & 0 \\ \hline
    \textbf{\# Items added} & 3'655'744 & 3'655'740 & 6'090'003 & 14'220 \\ \hline
    \textbf{Final Est. Card.} & 1'011 & 367 & 1'005 & 1 \\ \hline
\end{tabular}
\label{table:tab1}
\end{table}

\begin{table}[h]
\caption{Result of the attacks in the setting of \cite{hllvuln} over 30 iterations}
\begin{tabular}{| m{8.5em} | m{4em} | m{4em} | m{4em} | m{4em} |}
    \hline
    \textbf{Scenario} & \multicolumn{2}{c|}{S2} & \multicolumn{2}{c|}{S4} \\ \hline
    \textbf{Initial data?} & yes & no & yes & no \\ \hline
    \textbf{Original Est. Card.} & 1'004 & 0 & 998 & 0 \\ \hline
    \textbf{\# Items added} & 124'940 & 125'085 & 204'669 & 501 \\ \hline
    \textbf{Final Est. Card.} & 1'058 & 367 & 998 & 1 \\ \hline
\end{tabular}
\label{table:tab2}
\end{table}

>>>>

\section{Introduction}
Naive approaches to computing the cardinality of a big data set, such as sorting the elements or simply maintaining the set of unique elements seen, are impractical at scale. The HyperLogLog algorithm (HLL henceforth)~\cite{hll} is today the most widely used cardinality estimator. It is increasingly used in settings where adversaries may have  incentives to manipulate the estimate made by the algorithm. For example,~\cite{portscanhll} proposes its use for detecting network scanning attacks, while Facebook engineers have reported~\cite{fbhll} that they use HLL for estimating the number of active users. These applications demand a careful evaluation of the performance of HLL under adversarial input.

@@

\section{Overview of HLL}\label{sec:overview}
\subsection{The Algorithm}
HLL~\cite{hll} is a streaming algorithm based on the key observation that, for a stream of randomly distributed values represented as bit-strings of some fixed length, if we observe a value with the maximum of $k$ leading zero-bits, then the cardinality of the stream (i.e.\ the number of distinct values it contains) is likely to be on the order of $2^{k+1}$. In practice, to ensure a uniform distribution, the stream values are first processed by a hash function $h$ before the leading bits are inspected. So to estimate the cardinality of a stream, we need only store a representation of $k$, the length of the largest observed string of leading zero-bits for numbers in the stream. This provides a very compact mechanism for estimating the stream cardinality -- if the true cardinality is $N$, then just $\log\log(N)$ bits are needed to store the estimate.

This simple approach suffers from large variance in the estimation. In order to improve the estimate, we can use many estimators in parallel instead of one, and average the results. Each estimate is stored in its own bucket. The collection of buckets is referred to as the HLL \emph{sketch}. To map a value $x$ to one of $2^n$ buckets, \cite{loglog} suggests using the first $n$ bits of $h(x)$ as a bucket index, and then computing the longest sequence of leading zero bits on the remaining $\ell$ bits of $h(x)$ (so that the output length of $h(\cdot)$ is $n+\ell$). Estimators from all buckets are averaged using the harmonic mean and scaled by a constant $\alpha$, where $\alpha$ is empirically computed to correct a systematic multiplicative bias. As result, HLL is able to estimate cardinalities greater than $10^9$ with a typical standard error of 2\%, using only 1.5 kB of memory~\cite{hll}.

@@

\subsection{Applications}
For completeness and motivation, we provide examples of concrete uses of HLL:
\begin{itemize}
    \item Cardinality estimation provides a significantly faster way for Facebook to compute statistics on their users. They use HLL to find out how many distinct people visited their website in the past week~\cite{fbhll}.
    \item HLL has been proposed as a solution to detecting Denial-of-Service attacks~\cite{portscanhll} (this paper actually uses a variation on HLL called \emph{sliding HLL}~\cite{slidinghll} which estimates the cardinality over a moving time window). Specifically, HLL is used to count how many different ports are used as destination port over all packets received, as an attempt to identify when a port scan attack is underway.
    \item HLL has been implemented in network soft-switches to approximate the number of distinct packets in traffic flows and overcome the switch resource limits~\cite{flexswitch}. The number of unique flows traversing a switch can then be used to provide a better congestion control protocol.
\end{itemize}

@@

\subsection{Adversarial Setting}
We model four distinct adversarial scenarios based on the adversary's knowledge and capabilities. For all of them, we assume that the sketch already contains some existing data from honest users to simulate a real-life setting. Among the scenarios, the \textit{insider} setup of \cite{cardestprivacy} that we present as S4 makes the strongest assumptions about the adversarial capabilities since we assume that the attacker owns the data structure and thus has an exhaustive view on the sketch. %combines the knowledge of adversaries from S1 and S2.
\kenny{Not really! Because S1 is actually quite unrealistic, as we will argue below.}

\begin{itemize}
\item[S1:] The adversary has access to a \textit{test oracle} provided by the sketch owner, which allows him to submit an item and learn the hypothetical effect of inserting it into the sketch. He is then able to determine if inserting this item \textit{would} increase the cardinality estimation.

%The adversary is able to test the hypothetical effect of the insertion of an item on the cardinality estimation of the sketch. This can achieved via a \textit{test oracle} provided by the sketch owner, which allows an user to test the effect of an insertion on the cardinality estimate but without actually inserting the item, or if the attacker would gain access to a black-box replica of the sketch in use, i.e., buying the same switch and testing in the lab. %black-box access to the HLL in use -- that is, the adversary can ask for the HLL's cardinality estimate at any point in time, and so is able to check the effect on the cardinality estimate when inserting an item.
\kenny{TODO: clarify more what this is terms of a ''test oracle''; its stronger than described because the adverary can test the effect of an insertion without making the insertion!s}
\item[S2:] The adversary has access to the details of the HLL implementation, i.e., the adversary knows the number of buckets $2^n$ and the hash function $h$ in use, but is otherwise ``blind''. In particular, an S2 adversary does not have access to the values of the HLL cardinality estimate at any point in its attack. \mathilde{Would it make sense to add a sentence "This scenario would apply to~\cite{portscanhll}."?}
\item[S3:] The adversary has access to the details of the HLL implementation, i.e., the adversary knows the number of buckets $2^n$ and the hash function $h$ in use. Additionally, he can access and interact with the sketch via an API provided by the sketch owner, allowing him to insert an item or ask for the HLL's cardinality estimate at any point in time.
\kenny{TODO: The external attacker from~\cite{cardestprivacy}  described in terms of oracles.}
\item[S4:] The adversary has direct access to the HLL in use and all its internals, i.e., the number of buckets, the hash function $h$, and also the contents of each bucket in the HLL sketch. Recall that these buckets hold the intermediate estimators that are averaged in a later step to compute the final cardinality estimate. Again, an S4 adversary does not have access to the values of the HLL cardinality estimate at any point in its attack, but it can compute these values for itself (assuming its attack proceeds without input from other users being added to the HLL sketch in parallel with the attack). \mathilde{I am not sure about the last sentence. In the \textit{insider} model of \cite{cardestprivacy} the attacker owns the sketch so has access to both statistics (cardinality estimation) and counters in real time. So if he receives data coming from another user / notices an update in the counters, he can check reiterate over the discarded items and check whether he can retain some more? I know the goal of \cite{cardestprivacy} is different and there it makes sense to consider the scenario where the owner is malicious but not necessarily for us.}
\end{itemize}

Scenarios S1 and S2 are presented as M2 and M1, respectively, in~\cite{hllvuln} and S3 and S4 as the \textit{external} and \textit{internal} attack scenarios in \cite{cardestprivacy}.

We start by highlighting the fact that S1 seems unrealistic in practice, as there is no reason why a sketch owner would provide such \textit{test oracle}. The authors of \cite{hllvuln} argue that the assumptions of S1 could also be fulfilled if the attacker gains access to a replica of the machine the HLL is implemented on. The adversary could run tests on it, sequentially inserting, asking for the cardinality estimation and resetting the device, retaining only the items which do not increment the HLL estimate. \mathilde{Todo: Add sentence This second approach does not look much more convincing/practical.}
%This is unclear what this means in practice, since after insertion into the HLL sketch, an item cannot usually be removed by the adversary.
\kenny{Mathilde: can you think about this sentence that I added? Do we need to rewrite S1? The scenario does not really make sense at all in practice. I think we might use this to beat up the other paper a bit more.}

Furthermore, we show that although \cite{cardestprivacy} presents S3 and S4 as detached scenarios, the attacker with the capabilities of S3 can obtain the knowledge of S4. By analyzing which inputs increase the cardinality estimation, an attacker can easily recover the contents of each bucket in the sketch. To guess the estimator of a targeted bucket, the attacker gradually inserts items with an incrementing number of leading zeros in the $\ell$ rightmost bits of $h(x)$, until the cardinality estimation of the sketch increases. Once a change occurs, the attacker knows that the maximum number of leading zeros observed in that bucket just got updated to a value that can be recovered by looking at the last inserted item. The attacker can determine all estimators with $O(2^{n + \ell})$ pre-computations and $O(\ell \cdot 2^{n})$ insert and cardinality estimation queries. The fuller the sketch the most work the attacker has to provide.

@@

As the assumptions of S1 appear unrealistic and an attacker can escalate from the knowledge of S3 to the one of S4, we focus on the scenarios S2 and S4. We first present our attack in scenario S2, providing much stronger results than the corresponding attack of \cite{hllvuln}, and then use the additional information the adversary has access to in scenario S4 to make the attack even more powerful.

@@

\noindent\paragraph{Scenario S2} The adversary knows $h$ so it can adjust fields in the item $x$ it is trying to insert and keep only those for which the $\ell$ rightmost bits of $h(x)$ start with a one bit. In this case, the number of leading zero bits computed by the estimator of the destination bucket is always zero, so the estimator of this bucket is unlikely to be updated and the averaged approximate cardinality is likely to be left unchanged. For example, in the scenario of \cite{portscanhll}, the adversary could change the source port of its IP packet until it is satisfied with its hash value. Given sufficient flexibility in the input $x$, the adversary can insert many items into the HLL without increasing the cardinality markedly, by repeatedly sampling from the input domain.

\noindent\paragraph{Scenario S4} The adversary can adopt the same strategy as for S2, but make the attack more efficient and reduce the sampling requirements with the additional information available in this scenario (namely, the count values per bucket in the HLL sketch). So, it can allow some leading zero bits in the $\ell$ rightmost bits of $h(x)$ so long as this does not increase the current bucket estimate. In other words, if $h(x)$ is mapped to the $i$-th bucket with estimated cardinality $2^{c_i + 1}$ (because a value with $c_i$ leading zeroes was previously observed for this bucket), then, instead of the strict restriction of having a one bit in the first position in the $\ell$ rightmost bits of $h(x)$, the adversary is satisfied when there is a one bit in any of the first $c_i+1$ positions in this substring. In case the adversary hits an empty bucket (for which the estimator is 0), it must skip that bucket completely. Under these conditions, the estimators in the buckets are never updated, and there is no effect on the cardinality estimate made by HLL.  A special case arises when the HLL is completely empty at the beginning of the attack; here the adversary is forced to increase the estimate in at least one bucket, but with sampling this can obviously be done in such a way as to increase the HLL estimate to $2$ in a single bucket, leaving all the other buckets untouched.

@@

We assumed so far that there are already values coming from other honest users' data in the HLL. We now remove this assumption. The blind adversary in scenario S2 has no way to detect that it is attacking an empty HLL and cannot adapt its strategy, so all buckets that are hit will update their estimator once to $2^{0+1}=2$ items, leading to a final cardinality approximation of $\alpha2^{n+1}$ regardless of the number of items the adversary inserts. However, the adversary in S4 is able to detect that all buckets are empty and adapt its attack accordingly. The adversary can now target and fill one bucket only. This requires fixing $n+1$ bits of $h(x)$ for each input $x$, allowing the adversary to ``hide'' $2^{t-n-1}$ elements while keeping the HLL cardinality estimate to 1. Other work/cardinality-estimate trade-offs are of course possible.

@@

As a proof-of-concept, we implemented our attacks against the HLL implementation from \cite{clahll}. The attack code is available at \href{https://github.com/PizzaWhisperer/HLLVuln}{\textit{\url{https://github.com/PizzaWhisperer/HLLVuln}}}. For simplicity, our items are 4-character long ASCII strings, giving us up to 7,311,616 distinct items that can be inserted. We choose $h$ to be the 32-bit Murmur3 hash function from \cite{murmur3code}. \kenny{Why do we get to choose $h$? Isn't it fixed by the specific implementation we are attacking?} \mathilde{The library has a place holder for a 32 bit hash function but lets the user choose it. This was one of my concerns and I was wondering if it would make sense to attack \cite{datasketch} instead (hardcoded $h$, but when we discussed it, you said that due to Kerckhoff's principle, this hash function should be public so it does not matter that much.} We create an HLL sketch using $2^n = 256$ buckets and initialize it with 1,000 random items representing honest users' data.

@@

Those empirical results confirm our impact analysis on several points. First, when attacking a sketch already containing some items, we can see that the adversary is able to hide approximately half of the items' set under S2, and around 83\%%( $205$'$000 \approx 250'000 \times 0.82 \approx 250$'$000\times(1-\frac{1}{2\times H_c})$, with $H_c\approx\frac{1'000}{256}=3.9$).
$\approx (1-\frac{1}{2\times H_c})$ with $H_c\approx\frac{1'000}{256}=3.9$, under S4. Secondly, when attacking an empty sketch, the final cardinality estimate is always exactly 367 $=\alpha2^{n+1}$ with $\alpha = 0.72$ as specified by the Eq. (29) of \cite{hll} or 1 in respectively S2 and S4.

To assess the efficiency of our attacks, we can confront our results from Tab. \ref{table:tab2} with the attack presented in the Section 5.1 of \cite{hllvuln}, where they target the Redis \cite{redishll} open-source implementation of HLL and perform the attack against an empty sketch. Given a set of 250'000 items, the adversary could choose ``74'390 distinct items and obtain an HLL estimate of only 15'780``~\cite{hllvuln} achieving a five-fold reduction from the true cardinality. In comparison, the adversary following our strategy is able to add 125'000 distinct items while keeping the estimate at 367, demonstrating a reduction by a factor of 340.

\begin{table}[h]
\caption{Result of the attacks over 30 iterations}
\begin{tabular}{| m{8.5em} | m{4em} | m{4em} | m{4em} | m{4em} |}
    \hline
    \textbf{Adv. Scenario} & \multicolumn{2}{c|}{S2} & \multicolumn{2}{c|}{S4} \\ \hline
    \textbf{Initial data?} & yes & no & yes & no \\ \hline
    \textbf{Original Est. Card.} & 1'000 & 0 & 1'005 & 0 \\ \hline
    \textbf{\# Items added} & 3'655'744 & 3'655'740 & 6'090'003 & 14'220 \\ \hline
    \textbf{Final Est. Card.} & 1'011 & 367 & 1'005 & 1 \\ \hline
\end{tabular}
\label{table:tab1}
\end{table}

\begin{table}[h]
\caption{Result of the attacks in the setting of \cite{hllvuln} over 30 iterations}
\begin{tabular}{| m{8.5em} | m{4em} | m{4em} | m{4em} | m{4em} |}
    \hline
    \textbf{Adv. Scenario} & \multicolumn{2}{c|}{S2} & \multicolumn{2}{c|}{S4} \\ \hline
    \textbf{Initial data?} & yes & no & yes & no \\ \hline
    \textbf{Original Est. Card.} & 1'004 & 0 & 998 & 0 \\ \hline
    \textbf{\# Items added} & 124'940 & 125'085 & 204'669 & 501 \\ \hline
    \textbf{Final Est. Card.} & 1'058 & 367 & 998 & 1 \\ \hline
\end{tabular}
\label{table:tab2}
\end{table}
